Count pages completed in each year

### 2024-06-22 src/count_completed.Rmd
Update 2008 files

```{r md_links}
c_text <- "page_update: "
md_files$page_update_line <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) %>%
    str_subset(fixed(c_text)) %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
}
count(md_files, page_update_line)
count(md_files, yr, page_update_line)
```

>>>>

```{r md_links}
c_text <- "page_update: "
md_files$page_update_line <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) %>%
    str_subset(fixed(c_text)) %>%
    str_replace(c_text, "") -> page_update
  n <- length(page_update)
  if (n > 1) {
    cat(
      glue(
        "\n\n{n} duplicates found in {full_file_name}.\n\n"))}
  page_update %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
}
count(md_files, page_update_line)
# count(md_files, yr, page_update_line)
```

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    count(yr, page_update_line) %>%
    print
  cat("\n\n")
}
```

```{r}
test1 <- paste0("## " 1:5)
```

`r test1`
